Code used to generate paper results : Database comparison and CT characteristics

### 2024-05-17 Paper_code-CT_analysis.Rmd
Added legend in TCGA heatmap

```{r, echo = FALSE, eval = FALSE}
pdf(file = "figs/CT_met_AUC_hypo_TCGA.pdf", height = 2.3, width = 3)
draw(h1, column_title = "CT genes regulated by methylation",
     column_title_gp = gpar(fontsize = 5), show_heatmap_legend = FALSE,
     show_annotation_legend = FALSE)
dev.off()

>>>>

```{r, echo = FALSE, eval = FALSE}
pdf(file = "figs/CT_met_AUC_hypo_TCGA.pdf", height = 2.3, width = 3)
draw(h1, column_title = "CT genes regulated by methylation",
     column_title_gp = gpar(fontsize = 5), show_heatmap_legend = TRUE,
     show_annotation_legend = TRUE, heatmap_legend_side = "bottom",
     merge_legend = TRUE)
dev.off()
